A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
added conclusions on the classification methods.

// TODO: Tabela e descrição das diferentes taxas de erro

// TODO: Descrição de alguns padrões interessantes que sobressaiam nos modelos

>>>>

\begin{table}
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 19.80 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Bayesian Networks (Simulated Annealing) & 21.09 \\ \hline
    C4.5 & 21.69 \\ \hline
    Random Forest & 22.71 \\ \hline
    Bayesian Networks (Hill Climbing) & 22.93 \\ \hline
    CART & 25.37 \\ \hline
    Bayesian Networks (Genetic Search) & - \\ \hline
    \end{tabular}
    \caption{Error rates for the different algorithms used in the classification process}
    \label{tbl:overall_results}
    \end{center}
\end{table}

Table \ref{tbl:overall_results} summarizes the best error rates for the 
different algorithms used in the classification process. Each algorithm has 
different parameters to tweak it and the table only shows the best error rates
obtained. CN2 has the best results for this particular dataset, although it
takes longer than the majority of the other algorithms to build a classifier. 
ID3 and C4.5 are usually quick to process and build classifiers within a decent
error rate. ILP and CN2 build more expressive classifiers, capable of a better
interpretation by a human. One special note goes to Inductive Logic Programming,
a technique that allows the use of logic predicates to describe both the 
background knowledge and the produced model. The use of prolog enables the 
output produced by this technique to be better analyzed by a human agent. 
Another important conclusion of the conducted experimental process is that the 
worst error rate of the algorithms used is near 25\%, which denotes the power
of the current classification algorithms, capable of building relevant models in
a short period of time for relatively large datasets.

Analyzing the models produced, one can see that having a high capital gain 
clearly contributes to gaining more than 50K dollars per year. On the other
hand, part time workers usually don't gain more than 50K dollars per year, like
the younger and not married people.
